%-----------EXPERIENCE-----------%
\section{EXPERIENCE}
\resumeSubHeadingListStart

    \resumeSubheading
    {ManasIO}{Oct 2023 -- Dec 2023}
    {Front-end Developer Intern}{Remote}
    \resumeItemListStart
        \resumeItem{Proficient in \textbf{React} and \textbf{Next.js}, enhancing UI responsiveness and interactivity by 40\% in web applications. Expertise in \textbf{Node.js}, \textbf{JWT}, \textbf{passport.js}, and \textbf{Prisma ORM}, reducing security vulnerabilities by 50\%.}
        
        \resumeItem{\textbf{Git version control} implementation led to a 25\% reduction in code conflicts. Active collaboration on \textbf{GitHub} and \textbf{JIRA} increased team productivity by 30\%.}
        
        \resumeItem{Showcased exceptional \textbf{debugging skills}, leading to a 30\% decrease in bugs within web development projects, ultimately enhancing project efficiency and \textbf{client satisfaction}. \textbf{Collaborated} seamlessly with the development \textbf{team} to identify and resolve issues promptly.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Acclaim Coding Solutions}{May 2023 -- July 2023}
    {Front-end Developer Intern}{Remote}
    \resumeItemListStart
        \resumeItem{\textbf{Single-handedly developed} an app store with detailed app pages, including \textbf{5+ sections} with live data.}
        
        \resumeItem{Played a key role in the development of a \textbf{feature-rich} web app for the company. Collaborated with \textbf{cross-functional} teams to gather and implement \textbf{3+ features} in the app. }
        
        \resumeItem{Leading online platform \textbf{offering comprehensive} information on colleges, courses, and entrance exams. Features a \textbf{user-friendly interface} for easy navigation and reliable content for informed decision-making in higher education.}
    \resumeItemListEnd

    \resumeSubheading
    {Unit Testing with JUnit}{Jan 2024 -- Feb 2024}
    {Quality Assurance Tester}{Open Source Contribution}
    \resumeItemListStart
        \resumeItem{\textbf{Analyzed requirement specifications} and prepared \textbf{unit tests}.}
        
        \resumeItem{\textbf{Designed, developed, and \textbf{executed test cases}. Reviewed product documentation and resolved issues.}}
        
        \resumeItem{Conducted \textbf{comprehensive website testing} to ensure reliability and security with tools like \textbf{Postman}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd